Enter our title here

### 2017-08-29 manuscript.tex

DataCamp has the same reproducable capabilities as Swirl but is a web-based application; educators can
create their own courses that coincide with their lessons and students can access the course without having to install R.
Courses are available through the DataCamp website so students can access the lesson through their web-browser on their laptop,
tablet, or moble device. 
The DataCamp website offers pre-existing free community courses and specialized 'Premium' classes that you need to purchase. 
However, when used for academic purposes the premium DataCamp content is also free of charge.. (i'll come back to this).
Any college educator can create a classroom group on the DataCamp website, add student's to the group, assign pre-existing 
'community' courses and assign a course that they've created for the particular class.

The collection of community courses avaiable at DataCamp inlcude a wide range of topics from 'Introduction to R' to
'Quantitative Risk Management in R' so novice through advanced programming students will benefit.

@@

DataCamp can be used in the classroom in a number of ways: as traditional homework assignments, as an
activity during lab periods, as pre-class assignments for a flipped classroom, and even as a test or assessment tool.

@@

@@

The submission correctness testing code (or SCT) is the backbone for DataCamp's interactive nature. If a student submits an incorrect answer, they will 
receive immediate feedback on what they are doing wrong and the system will guide them to the right answer. Instructors can use the default feedback
that DataCamp automatically generates or write their own custom messages. The default feedback is meaningful and specific; most of the time custom messages
are not necessary unless there is a common problem that student are struggling with in which more unique feedback is necessary. DataCamp provides a helpful
R package called 'testwhat' which acts as a guide to writing the SCTs. 'testwhat' contains functions that can test different types of problems including
loops, object definitions, printed output, functions, ect (datacamp website), this submission correctness testing code compares the ideal answer (from the 
solution) to the students answer. Different arguements can be added to the test functions to alter the testing process and automatic feedback.

@@

The 'MultipleChoiceExercise', as you would expect, contains a question and a list of various answers. Instructors write the questions in the 'lesson' 
portion of the exercise and offer solutions in the 'Insruction' section. Like the 'normal' coding exercises, the lesson, instructions, pre-exercise code and
SCTs have to be specified but sample and solution code do not. There are two types of multiple choice questions, simple and regular. The simple multiple 
choice exercises are used for questions that do not require the R console or any R output. Regular multiple choice exercises allow instructors to pre
-program objects or plots that the student needs to access to answer the question. Both types of multiple choice exercises are straightforward to write can 
act as quick checks for understanding throughout the chapter.

>>>>

DataCamp has the same reproducable capabilities as Swirl but is a web-based application; educators can
create their own courses that coincide with their lessons and students can access the course without having to install R.
Courses are available through the DataCamp website and students can access the lesson through their web-browser on their laptop,
tablet or moble device, making the courses accessable to anyone with an internet connection. 
The DataCamp website offers pre-existing free community courses and specialized 'Premium' classes that you need to purchase. 
However, when used for academic purposes the premium DataCamp content is also free of charge.. (i'll come back to this).
Any college educator can create a classroom group on the DataCamp website, add student's to the group, assign pre-existing 
'community' courses and assign a course that they've created for the particular class.

The collection of community courses avaiable at DataCamp inlcude a wide range of topics from 'Introduction to R' to
'Quantitative Risk Management in R' so novice through advanced programming students will benefit.
DataCamp can be used in the classroom in a number of ways: as traditional homework assignments, as an
activity during lab periods, as pre-class assignments for a flipped classroom, and even as a test or assessment tool.

@@

@@

When starting to create a DataCamp course, it is helpful to view code from pre-existing community courses which can be found on GitHub.
You can use these files as a guide to build your own course or duplicate the repository and tailor the content to fit specific needs.
The DataCamp github repository contains links to the code for available courses; one of the most helpful when starting to build a course 
is 'datacamp/courses-intro-r' which contains the source files for the 'Intoduction to R' course.

- 'datacamp/testwhat' to help with submission correctness tests

@@

The submission correctness testing code (or SCT) is the backbone for DataCamp's interactive nature. If a student submits an incorrect answer, they will 
receive immediate feedback on what they are doing wrong and the system will guide them to the right answer. Instructors can use the default feedback
that DataCamp automatically generates or write their own custom messages. The default feedback is meaningful and specific; most of the time custom messages
are not necessary unless there is a common problem that student are struggling with in which more unique feedback is necessary. DataCamp provides a helpful
R package called 'testwhat' which acts as a guide to writing and using SCTs (this can be accessed on DataCamp's GitHub repository: 'datacamp/testwhat'). 
'testwhat' contains functions that can test different types of problems including loops, object definitions, printed output, functions, ect 
(datacamp website), this submission correctness testing code compares the ideal answer (from the solution) to the students answer. Different
arguements can be added to the test functions to alter the testing process and automatic feedback.

@@

The 'MultipleChoiceExercise', as you would expect, contains a question and a list of various answers. Instructors write the questions in the 'lesson' 
portion of the exercise and offer solutions in the 'Insruction' section. Like the 'normal' coding exercises, the lesson, instructions, pre-exercise code and
SCTs have to be specified but sample and solution code do not. DataCamp offers two types of multiple choice questions, simple and regular. The simple multiple 
choice exercises are used for questions that do not require the R console or any R output. Regular multiple choice exercises allow instructors to pre
-program objects or plots that the student needs to access to answer the question. Both types of multiple choice exercises are straightforward to write can 
act as quick checks for understanding throughout the chapter.
